\LARGE \bf ``Those Who Can't Do, Teach'': A Teachable Robotic Agent for Children Learning Handwriting

### 2014-10-03 main.tex
Last fixes

Preliminary in situ studies have been conducted with primary school classes to obtain
insight into children's use of the novel system. 
%The technical components of the system have been validated, in that children 
Children aged 6-8 were successfully 1) led to believe that the robot was
actually writing on the tablet, and 2) able to improve the robot's writing to a
level which they were satisfied with.

Furthermore, the system represents a
significant step towards an innovative use for robotics which addresses a
widespread and socially meaningful challenge in education, and provides context
for robotics in education beyond the well-explored use of teaching coding and
robotics-related subjects.

@@

    \item the potential for motor mimicry to yield significant improvements in
        handwriting interventions \cite{Berninger1997} further supports the case
        for investigating the use of a humanoid robot capable of physically
        demonstrating handwriting trajectories to its child learning partner.
\end{enumerate}
% * <deanna.m.hood@gmail.com> 2014-10-01T02:59:34.808Z:
%
% the article cited is not explained well enough
%
Consequently, the learning agent developed has been embodied in a commercially
affordable {\sc nao} humanoid robot. Its writing capabilities have been implemented by
leveraging synchronisation with a tablet display to simulate fine motor skills
otherwise infeasible for the robot.

@@

After determining the appropriate number of dimensions ($N$) for the shape
models, new letters can be generated by varying the parameter values in this
$N$-dimensional space in accordance with (\ref{eq:projection}). By choosing
parameter values which lie within the observed range in the dataset, it is
possible to produce letters which are more likely to be reasonable looking.
When the parameter values are outside of the range observed in the dataset, they
are less likely to represent shapes from the dataset of reasonable,
adult-written letters, and as a result are more likely to represent poor shapes.% * <deanna.m.hood@gmail.com> 2014-10-01T04:12:39.275Z:
%
% are adults legible?
%
Figure \ref{fig:sampleLetters} illustrates sample letters generated from the
models of `e' and `g' by selecting random values for the first 5 parameters 
from a distribution with
standard deviation of $3\sqrt\lambda_i$ rather than the $\sqrt\lambda_i$
standard deviation observed in the dataset.

@@

\begin{figure}[thpb]
    \centering
    \includegraphics[width=0.45\textwidth]{figures/learningSdemo}
    \caption{\label{fig:demonstrationShapes2}Example of the learning algorithm
    responding to user demonstration of shapes for the letter `s' (demonstrations received from two 7-8 year-old children).}% * <deanna.m.hood@gmail.com> 2014-10-01T04:25:20.590Z:
%
% confusing
%
\end{figure}

It is possible that parameters ${\bf p}^{(k)}$ and ${\bf p}_{demo}$, which
individually yield acceptable shapes, produce parameters ${\bf p}^{(k+1)}$
which yield an unacceptable shape. This is especially true if the demonstration
shape is of a different style to that learnt at time $k$ as there are no
restrictions imposed on parameter values. The proposed method for adapting to
the demonstration shape has the ability to recover, however: with further
demonstrations of the same letter, the system would eventually approach the
demonstration shape (Figure \ref{fig:eDemo}. As a result, the event of poor-looking 
intermediate letters
would not limit the interaction later proposed in Section \ref{sec:experiment}
in a technical sense, but it may influence the user's \emph{perception} of the learning
agent. It remains to be seen if it is necessary to avoid such an event
mathematically.

\begin{figure}[thpb]
    \centering
    \includegraphics[width=0.3\textwidth]{figures/learningEdemo}
    \caption{\label{fig:eDemo}Example of the learning algorithm
    responding to user demonstration of shapes for the letter `e', passing through a parameter state which yields a poor letter (demonstrations received from a 7-8 year-old child).}
\end{figure}

@@

The {\sc nao} humanoid robot, which has been developed by Aldebaran Robotics and 
purposely designed to look approachable \cite{Gouaillier2008}, has been used for
this work. It is a commercially affordable biped robot, 58cm tall, with 25
degrees of freedom, two cameras, speech capabilities and the ability to
autonomously execute a range of tasks.

@@

    \item reducing the number of points along the trajectory passed to the
        robot's motion planner, to improve timing accuracy, and

    \item not running computationally expensive tasks on the robot (such as
        camera publishing) while it is writing, as this interferes with the
        requested timings between points.

@@

To instruct the robot where to write, the robot has been configured to detect a
particular fiducial marker, a \emph{chilitag}\footnote{See
\url{https://github.com/chili-epfl/ros_markers} for more information on the
fiducial markers used.}, with the camera located in its head, and use that to
determine the relative position of the writing surface (Figure
\ref{fig:tabletDetection}). When used in an interaction involving a user, this
allows a user to move the tablet as required for the interaction. As publishing
the robot's camera has been identified as a computationally expensive task which
can disrupt the robot's timing of synchronised writing, it is only done when the
robot is not writing, and the tablet is assumed to be stationary during the
writing process.

@@

The fusion of the embodied handwriting agent developed with the handwriting
learning algorithm presented in Section \ref{sec:learningAlgorithm} involves the
integration of three components: the robot, the tablet, and a central controller
(Figure~\ref{fig:archi}).  The robot and Android tablet application present the
writing process/result to the user, as in Section \ref{sec:tabletSynch}.
Furthermore, the tablet application has been extended to act as the primary medium for
capturing user interaction, and publishes the user's demonstrations when user is
satisfied with their writing. The user demonstrations are received by the
interaction controller, running on a desktop computer. It is responsible for
getting the {\sc nao} to prompt and respond appropriately to feedback received, using
a finite state machine to manage the interaction stage and various system
inputs. The controller also manages the learning algorithm, by inferring the letter which
user demonstrations are for based on their position on the tablet, and
publishes the shapes to be written which are generated by the learning algorithm
in response to the feedback.

@@

The interaction context which has been developed as a framework for addressing
relevant research questions is one where participants are asked to improve the robot's
handwriting by correcting its letters. Figure~\ref{fig:pilotInteraction}
illustrates an example interaction sequence between the participant and the
robot, which consists of the following stages.

@@

    \item The robot responds to the word request verbally, and writes the
        letters by pointing at the tablet and imitating tracing the letters. The
        tablet, placed in front of the robot with a vertical, landscape orientation,
        displays the letters in synchronisation with the robot's movements.

    \item The robot asks for feedback from the participant and they demonstrate
        how to write the letter which they feel needs to be corrected. The
        demonstration is performed by drawing on the tablet with a stylus. The
        tablet may be moved into the most appropriate position for the child to
        write on it. Only one letter may be demonstrated at a time, and the
        position of the participant's demonstration on the tablet encodes the
        letter that it is a demonstration for. The participant can remove and
        repeat their letter if they are unhappy with it.
        %, or if it is in the wrong position as determined by the researcher
        %conducting the interaction
        When the participant is satisfied with the demonstration, a button on
        the tablet which signals that it is the robot's turn is pressed, and the
        demonstration is sent to the controller.

@@

A pilot study at the first school consisted of four groups of
approximately 8 english-speaking children, aged 6-7 years. The children
interacted with the system for a total of 65 minutes, with the robot writing 96
letters, 49 of which in response to demonstrations from the children.

As a result of the pilot study, two key observations were acted on. The first
was that children appeared to have a difficult time providing demonstrations to
the robot in the same place as previously-written letters. At the time, the
system required the children to write on top of a letter of the same type as the
one which they were demonstrating, and the children seemed to find this
counter-intuitive and would occasionally just trace the robot's letter as it
appeared. As such, the technical components of the system were extended to allow
the children the opportunity to write around previously-written letters instead
of just on top.

@@

The study at the second school involved 21 french-speaking students aged 7-8 years: 7 children
interacted with the robot by themselves, and 7 sessions included the remaining
14 students interacting with the robot in pairs. The duration of the sessions
was between 8 and 15 minutes, with an average of 11.4 minutes (SD = 2.3). % * <deanna.m.hood@gmail.com> 2014-09-05T09:25:41.865Z:
%
% We prompted them when time was short, didn't we? Or did they just say test
% whenever they wanted to...
%

@@

    \textbf{The simulated robotic writing was believed by the children in all
    cases.} There were, at times, 
    % * <deanna.m.hood@gmail.com> 2014-09-05T11:59:03.640Z:
    %
    % how many
    %
    questions about the robot's writing method at the beginning of the interaction,
    but when advised that the robot ``tells the tablet what it wants to write,''
    this was accepted by the children. To allow the children an opportunity to
    express doubt in the robot's ability to write without explicitly asking them if
    the robot was pretending, the children were asking if they believed that the
    robot would be able to write its name, \emph{{\sc nao}}, which had not previously been
    demonstrated. It was reasoned that this would prompt the children to question
    the point of the robot actually \emph{writing} if they had any suspicion that
    the robot was pretending, but this was never the case. In the event where the
    robot's writing was not correctly synchronised with the tablet, this did not affect the
    response of the child. If older children participate in the interaction study --
    which may be likely as children with lasting handwriting difficulties are included
    as participants -- it may become more important to invest time into the
    believability of the robot's writing scheme. However, for 6-8 year olds the
    proposed setup has been proven viable.

    \textbf{The children were engaged in teaching the robot.} % * <deanna.m.hood@gmail.com> 2014-09-05T09:54:48.069Z:
    %
    % maybe this is too strong as a 'conclusion' and should just be an observation. plus what does this even mean.. the child walking around the room was 'engaged' too...?
    %
    An average of 10.9 demonstration letters (SD = 4.4) were
    provided to the robot for each session during the interaction. Furthermore,
    in 9 out of the 14 sessions (64\%), the robot received demonstration letters
    \emph{after} reaching the test stage of the interaction. The participants'
    teaching after the test word had been written and evaluated -- the only
    purposefully imposed external motivation -- may suggest that by that time
    the participants had become intrinsically motivated to engage in the
    interaction.% * <deanna.m.hood@gmail.com> 2014-09-05T10:30:45.293Z:
    %
    % I guess it could have also come from us sitting there watching them
    %

    \textbf{All children believed that the robot was learning, and that
        they were the ones teaching it.} This was concluded from their responses
        when the children were asked directly. This is in contrast to a prior
        feasibility study for a version of the interaction which only allowed
        for touch-based feedback, not user demonstrations, in which three of the
        seven adult participants did not feel that it was their input which
        helped the robot improve.
        % * <deanna.m.hood@gmail.com> 2014-09-05T09:46:49.117Z:
    %
    % probably can't just casually mention this study without going into more detail...
    %

@@

A conclusion drawn in~\cite{Hoy2011} is that any 
handwriting intervention studies considered in the systematic review which involved 
fewer than two practice sessions per week and fewer than a total of 20 practice 
sessions, including homework, were not found to demonstrate effective results. This 
highlights the necessity to engage students in an interaction which will be sustainable
 over the long-term if we wish to move towards using the proposed system to answer 
research questions which involve the measurement of learning gains to gauge effectiveness. 
Several challenges are raised in developing such long-term capabilities for the system,
 from both technical and socialogical points of view. %not sure this makes sense

In terms of the interaction experience, the current experimental setting, while
technically autonomous, can not robustly recover from situations outside of the
nominal protocol (presented in Section~\ref{sec4}), and consequently still
requires the presence of an experimenter. The interaction state machine would
require extension in non-trivial ways to allow for long, fully autonomous
interactions with children.

In the current system, the robot can ask questions and prompt participants, but it 
cannot engage in discussions with the participants. It is clear that work is necessary 
to develop the conversational agent in the interaction so that the presence of an 
experimenter is not required for a captivating engagement. While there is the 
possiblity to focus the interaction design on group-based interaction with the robot 
in order to alleviate the necessity of a conversational agent, there is reason to 
believe that constructing such a social interaction is not a trivial task. Anectodes 
from the preliminary studies have shown that some children may criticise another's 
demonstrations to the robot, which may or may not be as damaging to a child's 
self-efficacy as when they are criticised in a typical educational context. In addition,
on occassions where a pair of children came to teach the robot different styles of a 
particular letter, they did not discuss with each other their different writing styles 
and the effect on the teaching efficiency. This may suggest that a social context in 
which verbalising opinions about differences is encouraged is necessary to get children 
to cooperate in teaching the robot.  
%- "Would have problems with the 'n'" - (8) projecting human learning characteristics.
%- awkward silence, speaking over the top of the robot to talk to experimenter....
%- Children saying the other was bad... (3, 9).
%- When one child wrote u differently to the other, they didn't discuss :(

@@

In the scope of open technical questions for enabling long-term interaction, it remains to be seen how shape models
for letters might be generated which capture the full range of mistakes typical
of children learning handwriting: extending the current system capable of
incorporating internal proportion and global deformation errors to one which can
also generate missing subparts of the letter, or break the letter down into
primitive strokes at will, for example. While we expect that incorporating a
database of letters drawn by children into the shape modeling process would
facilitate this, the current system has conceptual (a PCA only approach can not
generate or learn a different shape topology) and technical (no support for
multi-stroke shapes) limitations which need to be overcome.

If the system is extended to allow for a wider range of mistakes, a further question 
then is how the handwriting error
generation of the system may be abstracted to a higher level of control so that
a teacher may configure it to work with a child on a particular type of
mistakes, based on the child's performance. Where would the balance lie between
developing autonomous capabilities for the system to determine the child's
difficulties, and empowering the teaching staff to decide for themselves
instead?

With some of the challenges towards an engaging long-term handwriting intervention 
with the teachable robotic partner addressed, further steps can be made towards 
answering the ultimate question of what impact to the outcomes of interventions the 
addition of such a teachable robotic agent would have, including the effect on the 
participants' self-esteem, motivation, or learning gains. % does it impact the
%motivation of the participants, their self-esteem, and/or the learning gains
%that they experience? We are currently considering running a long-term study
%that would provide better evidences to answer these questions.

@@

\addtolength{\textheight}{-.0cm}   % This command serves to balance the column lengths
                                  % on the last page of the document manually. It shortens
                                  % the textheight of the last page by a suitable amount.
                                  % This command does not take effect until the next page
                                  % so it should come on the page before the last. Make
                                  % sure that you do not shorten the textheight too much.

@@

    \item developing capabilities for a robot with limited fine motor
        capabilities, such as the {\sc nao}, to engage in the act of handwriting in a
        way which is believable for interacting with children. This has been
        accomplished by leveraging simulated handwriting with a synchronised
        tablet;

    \item developing a system for generating poorly written letters appropriate
        for simulating a na\"ive learner in the context of handwriting, achieved
        by using statistical shape models through PCA of observations of the
        trajectory of the same letter;

@@

However, we believe that the strongest impact of this work for the human-robot
interaction community relates to the very \emph{nature} of the interaction
fostered by this research. The work presented here investigates a particular
role for a robot in the education of handwriting: not only the robot is actively
performing the activity (it draws letters), but it does so in a way that engages
the child in a very specific social role. The child is the teacher, the robot is
the learner: the child must engage in a (meta-)cognitive relationship with the robot
to try to understand why the robot fails and how to help it best.  Here, the
robot is not only an activity facilitator or orchestrator: its physical presence
and embodiment induce agency and anthropomorphising, and cognitively engage the
child into the learning activity, which we predict will lead to higher learning
efficacy.

Also notable, the robot is not used in the usual context of robotics or computer
education, but instead in an activity -- handwriting -- which requires fine
physical skills. In such activities, the embodied nature of the robot makes a
lot of sense (due to motor mimicry, the arm motion for instance is, \emph{by
itself}, part of the teaching). Along these lines, we hope to see more research
on non-STEM educational applications of robotics.

Beyond handwriting, we believe that this work provides a novel perspective on
the role for robots in the education landscape. \emph{Learning by teaching} is a
powerful paradigm because of not only its pedagogical efficacy, but its
potential to positively impact the child's motivation and self-esteem. We hope that 
this article shows that this is a very relevant context of use for robots. Indeed,
when facing a child with school difficulties, robots can play a role of a na\"ive 
learner which neither the adults nor the peers (because of the social effects it would 
induce) can convincingly play.

The strong social impact of early educational problems makes research in this field
an undoubtably meaningful challenge for HRI.

>>>>

Preliminary in situ studies have been conducted with primary school classes to obtain
insight into children's use of the novel system. 
%The technical components of the system have been validated, in that children 
Children aged 6-8 were successfully led to believe that the robot was
actually writing on the tablet, and were able to improve the robot's writing to a
level which they were satisfied with, validating the interaction.

Furthermore, the system represents a
significant step towards an innovative use for robotics which addresses a
wide-spread and socially meaningful challenge in education, and provides context
for robotics in education beyond the well-explored use of teaching coding and
robotics-related subjects.

@@

    \item the potential for motor mimicry to yield significant improvements in
        handwriting interventions in which letter formations are demonstrated to participants \cite{Berninger1997} further supports the case
        for investigating the use of a humanoid robot capable of physically
        demonstrating handwriting trajectories to its child learning partner.
\end{enumerate}

Consequently, the learning agent developed has been embodied in a commercially
affordable {\sc nao} humanoid robot. Its writing capabilities have been implemented by
leveraging synchronisation with a tablet display to simulate fine motor skills
otherwise infeasible for the robot.

@@

After determining the appropriate number of dimensions ($N$) for the shape
models, new letters can be generated by varying the parameter values in this
$N$-dimensional space in accordance with (\ref{eq:projection}). By choosing
parameter values which lie within the observed range in the dataset, it is
possible to produce letters which are more likely to be reasonable looking.
When the parameter values are outside of the range observed in the dataset, they
are less likely to represent shapes from the dataset of adult-written letters, 
and as a result are more likely to represent poor shapes.
Figure \ref{fig:sampleLetters} illustrates sample letters generated from the
models of `e' and `g' by selecting random values for the first 5 parameters 
from a distribution with
standard deviation of $3\sqrt\lambda_i$ rather than the $\sqrt\lambda_i$
standard deviation observed in the dataset.

@@

\begin{figure}[thpb]
    \centering
    \includegraphics[width=0.45\textwidth]{figures/learningSdemo}
    \caption{\label{fig:demonstrationShapes2}Example of the learning algorithm
    responding (top) to user demonstration of shapes (bottom) for the letter `s' (demonstrations received from two 7-8 year-old children taking turns).}
\end{figure}

It is possible that parameters ${\bf p}^{(k)}$ and ${\bf p}_{demo}$, which
individually yield acceptable shapes, produce parameters ${\bf p}^{(k+1)}$
which yield an unacceptable shape. This is especially true if the demonstration
shape is of a different style to that learnt at time $k$, as there are no
restrictions imposed on parameter values. However, the proposed method for adapting to
the demonstration shapes has the advantage of being able to recover from such a situation: with further
demonstrations of the same letter, the system would eventually approach the
demonstration shape (see Figure \ref{fig:eDemo}. As a result, the event of poor-looking 
intermediate letters
would not limit the interaction later proposed in Section \ref{sec:experiment}
in a technical sense, but it may influence the user's \emph{perception} of the learning
agent. It remains to be seen if it is necessary to avoid such an event
mathematically.

\begin{figure}[thpb]
    \centering
    \includegraphics[width=0.3\textwidth]{figures/learningEdemo}
    \caption{\label{fig:eDemo}Example of the learning algorithm
    responding (top) to user demonstration of shapes (bottom) for the letter `e', passing through a parameter state which yields a poor letter (demonstrations received from a 7-8 year-old child).}
\end{figure}

@@

The {\sc nao} V4 humanoid robot, which has been developed by Aldebaran Robotics and 
purposely designed to look approachable \cite{Gouaillier2008}, has been used for
this work. It is a commercially affordable biped robot, 58cm tall, with 25
degrees of freedom, two cameras, speech capabilities and the ability to
autonomously execute a range of tasks.

@@

    \item reducing the number of points along the trajectory passed to the
        robot's motion planner to improve timing accuracy, and

    \item not running computationally expensive tasks on the robot (such as
        camera publishing) while it is writing as this interferes with the
        requested timings between points.

@@

To instruct the robot where to write, the robot has been configured to detect a
particular fiducial marker, a \emph{chilitag}\footnote{See
\url{https://github.com/chili-epfl/ros_markers} for more information on the
fiducial markers used.}, with the camera located in its head, and to use that to
determine the relative position of the writing surface (Figure
\ref{fig:tabletDetection}). When used in an interaction involving a participant, this
allows a user to move the tablet as required for the interaction. As broadcasting
the robot's camera has been identified as a computationally expensive task which
can disrupt the robot's timing of synchronised writing, it is only done when the
robot is not writing, and the tablet is assumed to be stationary during the
writing process.

@@

The fusion of the embodied handwriting agent developed with the handwriting
learning algorithm presented in Section \ref{sec:learningAlgorithm} involves the
integration of three components: the robot, the tablet, and a central controller
(Figure~\ref{fig:archi}).  The robot and Android tablet application present the
writing process/result to the user, as in Section \ref{sec:tabletSynch}.
The tablet application has been extended to act as the primary medium for
capturing participant input, and publishes the user's demonstrations when they are
satisfied with their writing. The user demonstrations are received by the
interaction controller running on a desktop computer. It is responsible for
getting the {\sc nao} to prompt and respond appropriately to feedback received using
a finite state machine to manage the interaction stage and various system
inputs.  In the context of learning handwriting, an additional input to the system is a word 
from which the letters are to be learned, as detected by a fiducial marker on a word card.
The controller manages the learning algorithm by inferring the letter which
user demonstrations are intended for based on their position on the tablet, and
publishes the shapes to be written which are generated by the learning algorithm
in response to the feedback.

The source code for the teachable robotic handwriting partner has been made 
available at \url{https://github.com/chili-epfl/cowriter_letter_learning}.

@@

The interaction context which has been developed as a framework for addressing
relevant research questions is one where participants are asked to improve the robot's
handwriting by correcting its letters. Figure~\ref{fig:pilotInteraction}
illustrates an example interaction sequence between the participant and the
robot which consists of the following stages:

@@

    \item The robot responds to the word request verbally and writes the
        letters by pointing at the tablet and imitating writing the letters. The
        tablet, placed in front of the robot with a vertical, landscape orientation,
        displays the letters in synchronisation with the robot's movements.

    \item The robot asks for feedback from the participant and they demonstrate
        how to write the letter which they feel needs to be corrected. The
        demonstration is performed by drawing on the tablet with a stylus. The
        tablet may be moved into the most appropriate position for the child to
        write on it. Only one letter may be demonstrated at a time and the
        position of the participant's demonstration on the tablet encodes the
        letter that it is a demonstration for. The participant can remove and
        repeat their letter if they are unhappy with it.
        %, or if it is in the wrong position as determined by the researcher
        %conducting the interaction
        When the participant is satisfied with the demonstration, a button on
        the tablet which signals that it is the robot's turn is pressed and the
        demonstration is sent to the controller.

@@

A pilot study at the first school consisted of four groups of
approximately 8 english-speaking children, aged 6-7 years. The children
interacted with the system for a total of 65 minutes, with the robot writing 96
letters, of which 49 were in response to demonstrations from the children.

As a result of the pilot study, two key observations were acted on. The first
was that children appeared to have a difficult time providing demonstrations to
the robot in the same place as previously-written letters. At the time, the
system required the children to write on top of a letter of the same type as the
one which they were demonstrating, and the children seemed to find this
counter-intuitive and would occasionally just trace the robot's letter as it
appeared. As such, the technical components of the system were extended to allow
the children the opportunity to write around previously-written letters instead
of on top.

@@

The study at the second school involved 21 french-speaking students aged 7-8 years: 7 children
interacted with the robot individually and 7 sessions included the remaining
14 students interacting with the robot in pairs. The duration of the sessions
was between 8 and 15 minutes, with an average of 11.4 minutes (SD = 2.3). % * <deanna.m.hood@gmail.com> 2014-09-05T09:25:41.865Z:
%
% We prompted them when time was short, didn't we? Or did they just say test
% whenever they wanted to...
%

@@

    \textbf{The simulated robotic writing was believed by the children in all
    cases.} There were, at times, 
    % * <deanna.m.hood@gmail.com> 2014-09-05T11:59:03.640Z:
    %
    % how many
    %
    questions about the robot's writing method at the beginning of the interaction,
    but when advised that the robot ``tells the tablet what it wants to write,''
    this was accepted by the children. To allow the children an opportunity to
    express doubt in the robot's ability to write without explicitly asking them if
    the robot was pretending, the children were asked if they believed that the
    robot would be able to write its name, \emph{{\sc nao}} which had not previously been
    demonstrated. It was reasoned that this would prompt the children to question
    the point of the robot actually \emph{writing} if they had any suspicion that
    the robot was pretending, but this was never the case. In the event where the
    robot's writing was not correctly synchronised with the tablet, this did not affect the
    response of the child. If older children participate in the interaction study --
    which may be likely as children with lasting handwriting difficulties are included
    as participants -- it may become more important to invest time into the
    believability of the robot's writing scheme. However, for 6-8 year olds the
    proposed setup has been proven viable.

    \textbf{The children were engaged in teaching the robot.} % * <deanna.m.hood@gmail.com> 2014-09-05T09:54:48.069Z:
    %
    % maybe this is too strong as a 'conclusion' and should just be an observation. plus what does this even mean.. the child walking around the room was 'engaged' too...?
    %
    An average of 10.9 demonstration letters (SD = 4.4) were
    provided to the robot for each session during the interaction.
    In 9 out of the 14 sessions (64\%), the robot received demonstration letters
    \emph{after} reaching the test stage of the interaction. The participants'
    teaching after the test word had been written and evaluated -- the only
    purposefully imposed external motivation -- may suggest that by that time
    the participants had become intrinsically motivated to engage in the
    interaction.% * <deanna.m.hood@gmail.com> 2014-09-05T10:30:45.293Z:
    %
    % I guess it could have also come from us sitting there watching them
    %

    \textbf{All children believed that the robot was learning and that
        they were the ones teaching it.} This was concluded from the responses
        when the children were asked directly. This is in contrast to a prior
        feasibility study for a version of the interaction which only allowed
        for touch-based feedback, not user demonstrations, in which three of the
        seven adult participants did not feel that it was their input which
        helped the robot improve.
        % * <deanna.m.hood@gmail.com> 2014-09-05T09:46:49.117Z:
    %
    % probably can't just casually mention this study without going into more detail...
    %

@@

A conclusion drawn in~\cite{Hoy2011} is that any 
handwriting intervention studies considered in the systematic review which involved 
fewer than two practice sessions per week and fewer than a total of 20 practice 
sessions, including homework, were not found to demonstrate effective results. This 
highlights the necessity to engage students in an interaction which will be sustainable
 over the long-term in order to answer 
research questions which involve the measurement of learning gains. 
Several challenges are raised in developing such long-term capabilities for the system,
 from both technical and sociological points of view. %not sure this makes sense

In terms of the interaction experience, the current experimental setting, while
technically autonomous, can not robustly recover from situations outside of the
nominal protocol presented in Section~\ref{sec4}, and consequently still
requires the presence of an experimenter. The interaction finite state machine would
require extension in non-trivial ways to allow for long, fully autonomous
interactions with children.

In the current system, the robot can ask questions and prompt participants, but it 
cannot engage in discussions with the participants. It is clear that work is necessary 
to develop the conversational agent in the interaction so that the presence of an 
experimenter is not required for a captivating and continuing engagement. While there is the 
possiblity to focus the interaction design on group-based interaction with the robot 
in order to alleviate the necessity of a conversational agent, there is reason to 
believe that constructing such a social interaction is not a trivial task. Anecdotes 
from the preliminary studies have shown that some children may criticise another's 
demonstrations to the robot, which may or may not be as damaging to a child's 
self-efficacy as when they are criticised in a typical educational context. In addition,
on occassions where a pair of children came to teach the robot different styles of a 
particular letter, they did not discuss with each other their different writing styles 
and the effect on the teaching efficiency. This may suggest that a constructed social context in 
which verbalising opinions about differences is encouraged may be necessary to get children 
to cooperate in teaching the robot in a group setting.  
%- "Would have problems with the 'n'" - (8) projecting human learning characteristics.
%- awkward silence, speaking over the top of the robot to talk to experimenter....
%- Children saying the other was bad... (3, 9).
%- When one child wrote u differently to the other, they didn't discuss :(

@@

In the scope of open technical questions for enabling long-term interaction, it remains to be seen how shape models
for letters might be generated which capture the full range of mistakes typical
of children learning handwriting. This includes extending the current system capable of
incorporating internal proportion and global deformation errors to one which can
also generate missing subparts of the letter, or break the letter down into
primitive strokes, for example. While it is expected that incorporating a
database of letters drawn by children into the shape modeling process would
facilitate this, the current system has conceptual -- a PCA-only approach can not
generate or learn a different shape topology -- and technical -- no support is currently implemented for
multi-stroke shapes -- limitations which would need to be overcome.

If the system is extended to allow for a wider range of mistakes, a further 
topic for exploration then is how the handwriting error
generation of the system may be abstracted to a higher level of control so that
a teacher may configure it to work with a child on a particular type of
mistakes based on the child's performance. Where would the balance lie between
developing autonomous capabilities for the system to determine the child's
difficulties and empowering the teaching staff to decide for themselves
instead?

With some of the challenges towards an engaging long-term handwriting intervention 
with the teachable robotic partner addressed, further steps can be made towards 
answering the central question of what impact to the outcomes of interventions the 
addition of such a teachable robotic agent would have, including the effect on the 
participants' self-esteem, motivation, and learning gains. % does it impact the
%motivation of the participants, their self-esteem, and/or the learning gains
%that they experience? We are currently considering running a long-term study
%that would provide better evidences to answer these questions.

@@

\addtolength{\textheight}{-.5cm}   % This command serves to balance the column lengths
                                  % on the last page of the document manually. It shortens
                                  % the textheight of the last page by a suitable amount.
                                  % This command does not take effect until the next page
                                  % so it should come on the page before the last. Make
                                  % sure that you do not shorten the textheight too much.

@@

    \item developing capabilities for a robot with limited fine motor
        capabilities, in particular the {\sc nao} robot, to engage in the act of handwriting in a
        way which is believable for interacting with children. This has been
        accomplished by leveraging simulated handwriting with a synchronised
        tablet communicating via ROS;

    \item developing a system for generating poorly written letters appropriate
        for simulating a na\"ive learner in the context of handwriting, achieved
        by using statistical shape models through PCA of observations of the
        trajectory of the same letter;% * <deanna.m.hood@gmail.com> 2014-10-03T00:52:47.503Z:
%
% this is pretty "done before" so might want to play it down
%

@@

However, we believe that the strongest impact of this work is for the human-robot
interaction community and relates to the very \emph{nature} of the interaction
fostered by this research. The work presented here investigates a particular
role for a robot in the education of handwriting: not only is the robot actively
performing the activity by drawing letters, but it does so in a way that engages
the child in a very specific social role. The child is the teacher in this relationship and the robot is
the learner: the child must engage in a (meta-)cognitive relationship with the robot
to try to understand why the robot fails and how to help it best.  Here, the
robot is more than just an activity facilitator or orchestrator -- its physical presence
and embodiment induce agency and anthropomorphising, and cognitively engage the
child into the learning activity, which we predict will lead to higher learning
efficacy.

Also notable, the robot is not used in the usual context of robotics or computer
education, but instead in an activity -- handwriting -- which requires fine
physical skills. In such activities, the embodied nature of the robot is appropriate as in interventions where motor mimicry is elicited \cite{Berninger1997} the arm motion for instance is, \emph{by
itself}, part of the teaching. Along these lines, we hope to see more research
on non-STEM educational applications of robotics.

Beyond handwriting, we believe that this work provides a novel perspective on
the role for robots in the field of education. \emph{Learning by teaching} is a
powerful paradigm because of not only its pedagogical efficacy, but its
potential to positively impact the child's motivation and self-esteem. We hope that 
this article shows that this is a very relevant context of use for robots. Indeed,
when facing a child with school difficulties, robots can play the role of a na\"ive 
learner which neither adults nor peers -- because of the social effects it would 
induce -- can convincingly play.

The strong social impact of early educational problems makes continued research in this field
an undoubtably meaningful challenge for robotics and human-robot interaction.
